\Large \bf Evaluating eBPF as a Platform for Congestion Control Algorithm

### 2024-12-07 paper/sections/evaluation.tex

\documentclass[../main.tex]{subfiles}
\begin{document}
Design
\end{document}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
In order to make sure we are correctly benchmarking the performance impact of CCAs rather than miscellneous confounding factors, we ran the benchmark on an out-of-the-box Debian image on a VM. To ensure the CPU benchmark and the CCA are running on the same CPU, our VM is set up to contain only one core. We also decided to run our benchmarks on various implementations of TCP Cubic due to its wide availability across platforms. \\
The results of behavioral benchmarks are shown in Figure \ref{fig:behavioral}. From the graph, we can see that [to-be-added-conclusion]. The results of CPU benchmarks are shown in Figure \ref{fig:cpu}. The eBPF implementation of TCP Cubic achieved impressive CPU performance compared to the built-in Linux kernel networking stack implementation. CCP-Cubic from the CCP Project (cite generic-cong-avoid git repo) combined with the kernel module + netlink CCP datapath achieved slightly lower performance, where its median is at x percent of the full kernel implementation value. Our implementation of eBPFCCP ranked lower on the performance chart, but was still able to achieve y percent of the full kernel implementation value. Due to the relative comparability of CPU performance between the kernel and eBPF implementations of TCP Cubicm, we theorize the noticable gap between eBPFCCP and kernel module CCP was due to our choice of using unix pipes rather than netlink as a channel for communicating between the eBPFCCP and the user space program. \\
From these results, we can conclude that eBPF is a viable platform for the development CCAs. The negligible performance overhead when compared to the kernel native implementation is impressive, and suggests that eBPF-CCAs can possibly also be used as a long-term deployment option outside of research and development stages. 
\end{document}

### 2024-12-07 paper/sections/relatedwork.tex

\documentclass[../main.tex]{subfiles}
\begin{document}
CCP decoupled data gathering and CCA computation. A datapath module gathers information regarding a TCP flow and sends it to user space via various methods (such as netlink sockets and unix pipes), while a user space program listens to the given data and sends back any updates to be made to the TCP connection state. Platform/OS independence
\end{document}

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
In order to fully evaluate performance of eBPF-based CCAs against alternative approaches, we looked at prior research aimed at reducing CCA-development overhead. Specifically, the Congestion Control Plane was developed to be an abstraction layer where developers can experiment with new CCA ideas without worrying about the intricacies of kernel networking stacks. Most notably, CCP decoupled data gathering and CCA computation. A datapath module gathers information regarding a TCP flow and sends it to user space via various channels, such as netlink sockets and unix pipes. A user space program then listens to the provided data and sends back any updates to be made to the TCP connection state. Since the computation lives in user space, developers are shielded from the potential of introducing kernel-crashing bugs as long as the underlying CCP datapath implementation is safe. The separation of data-gathering and computation also allows for further platform/OS independence. While traditional CCAs are tightly coupled with the kernel networking stack they are developed on top of, CCP allows for the same CCA to be run on different platforms with minimal changes. A CCP-based CCA can be directly ran on a completely different host, as long as there exists an existing datapath that implements the CCP standard API. \\ 
Due to CCP's datapath-reliant nature, the performance of any CCP-based congestion control will heavily depend on the implementation of the underlying datapath, as well as the channel used to communicate between user space and kernel space. In our investigations to test the performance of CCP-based CCAs, we decided to build an alternative datapath module that is implemented as an eBPF program rather than a kernel module. In addition to providing more safety guarantees, this implementation also allows us to test how the performance of CCP-based CCAs can vary depending on the underlying datapath implementation. \\

\end{document}
